Resurgence of the Airy function

### 2022-07-04 airy-resurgence.tex
Start sketching solutions for singular integral equations

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
\end{align*}
so
\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
In particular, when $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, 0)$.
\subsection{Order shifting}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

>>>>

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
\end{align*}
so
\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
\subsubsection{Fractional integral equations near a regular singular point}
Consider an integral operator $\mathcal{J}$ of the form
\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
where:
\begin{itemize}
\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
\item $p$ has a first-order zero at $\zeta = 0$.
\end{itemize}

\textcolor{DodgerBlue}{We want to solve the equation $\mathcal{J}f = 0$. Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty}(\Omega)$.}

\color{SeaGreen}
\begin{prop}\label{prop:frac-mollify}
If $f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^\alpha)$ with $\alpha \in (-1, \infty)$, then $\partial^\lambda_{\zeta \text{ from } 0}\,f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^{\alpha-\lambda})$ for all $\lambda \in (-\infty, 0)$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{SeaGreen}
\begin{prop}\label{prop:frac-int-growth}
For any $f \in \holoL{\infty}(\Omega)$ and $\lambda \in (-\infty, 0)$, the bound
\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\,f\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \|f\|_\infty \]
holds pointwise throughout $\Omega$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{black}

Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$. Since $p$, $q$, and $r_\lambda$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
p & = p'_0 \zeta &\;+\;& \tilde{p} \zeta^2 \\
q & = q_0 &\;+\;& \tilde{q} \zeta \\
\textcolor{orange}{r_\lambda} & = r_{\lambda,0} &\;+\;& \tilde{r}_\lambda \zeta,
where $\tilde{p}, \tilde{q} \in \holoL{\infty}(\Omega)$ extend holomorphically over $\zeta = 0$ too. For any $\tau \in (0, \infty)$,
\mathcal{J} \zeta^{\tau-1} & = p'_0 \zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(q_0 \zeta^{\tau-1}\big) + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big) \\
& = (p'_0 + q_0/\tau)\zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).
Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
\mathcal{J} \zeta^{\tau-1} & = \textcolor{SeaGreen}{\tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).} \\
\mathcal{J} \zeta^{\tau-1} & = \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_{\lambda,0} \zeta^{\tau-1} + \tilde{r}_\lambda \zeta^\tau\big) \\
& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-1-\lambda} + \partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right]} \\
& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-(\lambda+1)} \right] + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau.}
Now we can rewrite the equation $\mathcal{J}(\zeta^{\tau-1} + \tilde{f}) = 0$ as
\mathcal{J} \zeta^{\tau-1} + \left[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = 0 \\
\mathcal{J} \zeta^{\tau-1} + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = -p\tilde{f}.
Observing that
\[ \frac{1}{p} = \frac{\zeta^{-1}}{p_0 + \tilde{p} \zeta}, \]
\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} + \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right] \right] \\
\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} \right] \right] + \frac{1}{p_0 + \tilde{p} \zeta} \left[ \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau
Proposition~\ref{prop:frac-int-growth} guarantees that
\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \le |\zeta|\,\big\|\tilde{q} \zeta^\tau\big\|_\infty, \]
so
\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \\
& \le \big\|\tilde{q} \zeta^\tau\big\|_\infty \\
& \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty.
Similarly,
\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty, \]
so
\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \\
& \le (-\tfrac{1}{\lambda}) |\zeta|^{-(\lambda+1)} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty \\
& \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{-(\lambda+1)}\big\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
& = \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty.
In short,
\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big\|_\infty & \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big\|_\infty & \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty
\subsection{Order shifting}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
